### 2021-06-04 README.Rmd
Update to dependancies (hms for plots).

Note that `onsetsync` is not dedicated to extraction of onsets from audio as that can be done in other packages (e.g. [Librosa](https://librosa.org), or [Mir Toolbox for Matlab](https://www.jyu.fi/hytk/fi/laitokset/mutku/en/research/materials/mirtoolbox), or [Sonic Visualiser](https://www.sonicvisualiser.org) using well-known onset detection algorithms. Here we take it as granted that we have extracted the onsets in some of these programs, probably checked them by hand, and we have the onset times recorded into the csv files.

>>>>

Note that `onsetsync` is not dedicated to extraction of onsets from audio as that can be done in other packages (e.g. [Librosa](https://librosa.org), or [Mir Toolbox for Matlab](https://www.jyu.fi/hytk/fi/laitokset/mutku/en/research/materials/mirtoolbox), or [Sonic Visualiser](https://www.sonicvisualiser.org) using well-known onset detection algorithms. Here we take it as granted that we have extracted the onsets in some of these programs, probably checked them by hand, and we have the onset times recorded into csv files.
